Supporting Information

### 2021-10-22 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
ROB update

rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
rob_records <- rob_records[rob_records$record_id < "5566", ]

@@

p6 <- occupationalset_rob_trafficlight +
  ggplot2::labs(
    caption = "
    Domains:
  D1: Representativeness of the sample (selection bias)
  D2: Characteristics of non-respondents (selection bias)
  D3: Symptom assessment (information bias)
  D4: Recording of symptoms (information bias)
  D5: Classification of asymptomatic status (misclassification bias)
  D6: Selective reporting of symptoms status (attrition bias)")

@@

p8 <- q2_rob_trafficlight +
  ggplot2::labs(
    caption = "
    Domains:
  D1: Representativeness of the sample (selection bias)
  D2: Characteristics of non-respondents (selection bias)
  D3: Symptom assessment (information bias)
  D4: Recording of symptoms (information bias)
  D5: Classification of asymptomatic status (misclassification bias)
  D6: Selective reporting of symptoms status (attrition bias)")

>>>>

rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
#rob_records <- rob_records[rob_records$record_id < "5566", ]
rob_records <- rob_records[rob_records$record_id < 5296, ]

@@

p6 <- occupationalset_rob_trafficlight +
  ggplot2::labs(
    caption = "
    Domains

    Selection Bias:
  D1.1: Representativeness of the sample
  D1.2: Characteristics of non-respondents
    Information Bias:
  D2.1: Symptom assessment
  D2.1: Recording of symptoms
    Misclassification bias:
  D3: Classification of asymptomatic status
    Attrition bias:
  D4: Selective reporting of symptoms status")

@@

p8 <- q2_rob_trafficlight +
  ggplot2::labs(
    caption = "
    Domains

    Selection Bias:
  D1.1: Representativeness of the sample
  D1.2: Characteristics of non-respondents
    Information Bias:
  D2.1: Symptom assessment
  D2.1: Recording of symptoms
    Misclassification bias:
  D3: Classification of asymptomatic status
    Attrition bias:
  D4: Selective reporting of symptoms status")
